Manuscript Figures

### 2024-05-22 code/Manuscript_figures.rmd
add figure path, add new library for sankey diagram

---
title: "Manuscript Figures"
author: "Hazel J. Anderson"
project: "Plant-Frugivore Diversity"
collaborators: "Beth E. Gerstner, Phoebe L. Zarnetske"
overview: "This script generates misc figures for manuscript that corresponds to this project."
data input: ""
data output: ""
date: "2024-05-14"
output: 
    html_document:
      code_link: TRUE
      code_download: TRUE
---

# Load required packages

```{r}
library(ggplot2)
library(tidyverse)
library(dplyr)
library(tidyr)
# devtools::install_github("pedropark99/ggfunnel")
library(ggfunnel)
library(ggpubr)
```

@@

# References
```{r}
library(report)
cite_packages()
```

# Session Info
```{r, class.source= 'fold-hide'}
devtools::session_info()
```

>>>>

---
title: "Manuscript Figures"
author: "Hazel J. Anderson"
project: "Plant-Frugivore Diversity"
collaborators: "Beth E. Gerstner, Phoebe L. Zarnetske"
overview: "This script generates misc figures for manuscript that corresponds to this project."
data input: ""
data output: ""
date: "2024-05-14"
output: 
    html_document:
      code_link: TRUE
---

# Set file paths
```{r}
figure_path <- file.path('G:/Shared drives/SpaCE_Lab_FRUGIVORIA/data/plants/figures')
```

# Load required packages
```{r}
library(ggplot2)
library(tidyverse)
library(dplyr)
library(tidyr)
# devtools::install_github("pedropark99/ggfunnel")
library(ggfunnel)
library(ggpubr)
library(networkD3)
```

@@

# Create Sankey diagram for 
Inspiration figures: https://conbio-onlinelibrary-wiley-com.proxy2.cl.msu.edu/doi/10.1111/csp2.311#csp2311-fig-0003 and https://bsapubs-onlinelibrary-wiley-com.proxy2.cl.msu.edu/doi/full/10.1002/aps3.11575#aps311575-fig-0003

```{r}

```

# References

```{r}
library(report)
cite_packages()
```

<details>

<summary><h1>Session Info</h1></summary>

```{r, class.source= 'fold-hide'}
devtools::session_info()
```

</details>
